Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-15 manuscript.Rmd
remove causal language closes #263

A single simulated dataset already helps to ensure that the plan is viable under certain circumstances.
However, repeated simulation with varying parameters, a so-called Monte Carlo simulation, lets researchers play through several scenarios.
Monte Carlo simulation lets researchers navigate several trade-offs regarding their resources.
In the simplest case, they can assess the power (the probability to detect an effect of a given size) for varying numbers of observations in the simulation to determine the required sample size for their study [@brandmaier2018precision].
@bakkerRecommendationsPreregistrationsInternal2020 found that a formal power analysis does not increase the planned sample size on average but can help to invest resources more efficiently.
Researchers may also evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].

>>>>

A single simulated dataset already helps to ensure that the plan is viable under certain circumstances.
However, repeated simulation with varying parameters, a so-called Monte Carlo simulation, lets researchers play through several scenarios.
Monte Carlo simulation lets researchers navigate several trade-offs regarding their resources.
In the simplest case, they can assess the power (the probability to detect an effect of a given size) for varying numbers of observations in the simulation to determine the required sample size for their study [@brandmaier2018precision].
@bakkerRecommendationsPreregistrationsInternal2020 found that a formal power analysis may help researchers to invest resources more efficiently.
Researchers may also evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].
